---
output:
  pdf_document: default
  html_document: default
---
```{r, echo=FALSE}
knitr::opts_chunk$set(error = TRUE)
```

```{r setup, include=FALSE}
chooseCRANmirror(graphics=FALSE, ind=1)
knitr::opts_chunk$set(echo = TRUE)


```

```{r,echo=FALSE,include=FALSE}
library(plyr)
library(readr)
library(lubridate)
library(dplyr)
library(tidyr)
library(ggplot2)
```



# Statistical Analysis

US Consumer Complaints dataset contains 18 vaiables. Most of the variales like company,product,sub_product,issue and sub_issue are considered as categorical varaibles

##Chi-square Tests

Chi-Square tests assumes a null hypothesis and an alternate hypothesis. If the p-value is less than the pre-determinded value (0.05) then null hypothesis will be rejected.The conclusion is those two categorical values are dependent.


####Reading the data

```{r}
complaint <- read_csv("consumer_complaints.csv")
comp_prod <- table(complaint$company,complaint$product)
complaint$product<-as.factor(complaint$product)
complaint$company<-as.factor(complaint$company)
complaint$sub_product<-as.factor(complaint$sub_product)
complaint$issue <- as.factor(complaint$issue)
complaint$submitted_via <- as.factor(complaint$submitted_via)

```

##Chi-Square tests

Company and Product are dependent.

```{r}
chisq.test(complaint$company,complaint$product,correct = FALSE)
```

```{r}
chisq.test(complaint$issue,complaint$submitted_via,correct = FALSE)
```

From above results issue and subitted_via also dependent variables

```{r}
comp_disp <- complaint %>%
  select(company,`consumer_disputed?`)%>%
  na.omit()

comp_disp_table <- table(comp_disp$company,comp_disp$`consumer_disputed?`)

chisq.test(comp_disp_table,correct = FALSE)

chisq.test(complaint$company,complaint$`consumer_disputed?`,correct = FALSE)


chisq.test(complaint$timely_response,complaint$`consumer_disputed?`,correct = FALSE)

```

The variables for which chi-squared tests are considered are proven to be dependent.

